GSE158422: DNA methylation in Lung squamous cell carcinoma - RNA expression and integration

### 2023-12-09 figs/GSE158422_rna_int.Rmd
rna int

suppressPackageStartupMessages({
  library("DESeq2")
  library("eulerr")
  library("IlluminaHumanMethylation450kmanifest")
  library("IlluminaHumanMethylationEPICanno.ilm10b4.hg19")
  library("tictoc")
  library("limma")
  library("mitch")
  library("kableExtra")
  library("beeswarm")
  library("missMethyl")
  library("HGNChelper")
  library("gplots")
})

@@

@@

@@

@@

>>>>

suppressPackageStartupMessages({
  library("DESeq2")
  library("eulerr")
  library("IlluminaHumanMethylation450kmanifest")
  library("IlluminaHumanMethylationEPICanno.ilm10b4.hg19")
  library("tictoc")
  library("limma")
  library("mitch")
  library("kableExtra")
  library("beeswarm")
  library("missMethyl")
  library("HGNChelper")
  library("gplots")
  library("ggplot2")

})

@@

p3 <- heatmap.2( as.matrix(mtop) , trace="none",margins = c(6,25), col=colfunc(25), cexRow=.6, cexCol=1)

@@

p1 <- plot(euler(vg),quantities=TRUE)

@@

p2 <- plot(euler(vm),quantities=TRUE)

@@

## Assemble figure

Grid arrange function.

```{r,gridarrange}

plot5 <- grid.arrange(arrangeGrob(p1, p2, ncol=1), p3,
  ncol=2, widths=c(1,1))
